\bfseries\LARGE\singlespacing{Transmission of respiratory viral infections with and without air cleaners in a Swiss school under non-pandemic conditions in 2023: A modeling study of epidemiological, environmental, and molecular data}

### 2023-10-17 doc/paper/manuscript-lancet.tex
Updates from Overleaf

\noindent All analyses were performed in R software (version 4.2.0)\cite{RCoreTeam2022} and modeling in Stan (version 2.21.0)\cite{Carpenter2017}. Model parameters were estimated with a Bayesian approach, using the Hamiltonian Monte Carlo algorithm with the No-U-Turn Sampler (NUTS)\cite{Hoffman2014}. %Each model is estimated with 4 Markov chains and 2,000 iterations of which the first 1,000 iterations are discarded as part of the warm-up. Estimation power is evaluated via the effective sample size (ESS) and convergence of the Markov chains is evaluated with the Gelman-Rubin convergence diagnostic ($\hat{R}$). 
If not stated otherwise, we report posterior means and credible intervals (CrIs) based on the 50\%, 80\%, and 95\% quantiles of the posterior samples, respectively. The code is available from \url{https://osf.io/38j9g}.

@@

Absences related to respiratory infections were less frequent with air cleaners (\cref{fig:infection-risk}c). Overall, there were 22~respiratory cases without and 13~cases with air cleaners. Based on our Bayesian latent variable hierarchical regression model, the posterior probability that air cleaners reduced the risk of infection was 90.8\%, suggesting a beneficial effect of air cleaners. However, the decrease in the risk of infection was small (adjusted relative risk 0.72, 95\%-CrI 0.44 to 1.15). As a result, the estimated number of infections would be 36 (95\%-CrI 21 to 64) if air cleaners had been installed throughout the study period, compared to 62 (95\%-CrI 29 to 141) infections if air cleaners had not been installed (\supp~\zref{fig:avoided-infections}). Detailed estimations are provided in the \supp~text~\zref{sec:detailed-redcap}.

@@

\begin{figure}[!htpb]
\centering
    \includegraphics{../../results/mol-data/saliva-by-study-condition.pdf}\hspace{1.5cm}
    \includegraphics{../../results/env-data/aerosol-number-boxplot.pdf}
    \includegraphics{../../results/epi-data/cases_by_condition.pdf}\hspace{1.5cm}
    \includegraphics{../../results/cough-data/coughs-frequency-by-condition.pdf}
    \caption{\textbf{Risk of infection by study condition}. \textbf{(a)}~Number of positive saliva samples. \textbf{(b)}~Daily average aerosol number concentrations as boxplots. \textbf{(c)}~Number of respiratory cases. \textbf{(d)}~Daily average number of detected coughs per minute.}
    \label{fig:infection-risk}
\end{figure}

>>>>

\noindent All analyses were performed in R software (version 4.2.0)\cite{RCoreTeam2022} and modeling in Stan (version 2.21.0)\cite{Carpenter2017}. Model parameters were estimated with a Bayesian approach, using the Hamiltonian Monte Carlo algorithm with the No-U-Turn Sampler (NUTS)\cite{Hoffman2014}. %Each model is estimated with 4 Markov chains and 2,000 iterations of which the first 1,000 iterations are discarded as part of the warm-up. Estimation power is evaluated via the effective sample size (ESS) and convergence of the Markov chains is evaluated with the Gelman-Rubin convergence diagnostic ($\hat{R}$). 
If not stated otherwise, we report the posterior probability (PP), mean, and 95\%credible interval (CrI) of the posterior samples. The code is available from \url{https://osf.io/38j9g}.

@@

Absences related to respiratory infections were less frequent with air cleaners (\cref{fig:infection-risk}c). Overall, there were 22~respiratory cases without and 13~cases with air cleaners. Based on our Bayesian latent variable hierarchical regression model, the posterior probability that air cleaners reduced the risk of infection was 91\%, suggesting a beneficial effect of air cleaners. However, the decrease in the risk of infection was small (adjusted relative risk 0.72, 95\%-CrI 0.44 to 1.15). As a result, the estimated number of infections would be 36 (95\%-CrI 21 to 64) if air cleaners had been installed throughout the study period, compared to 62 (95\%-CrI 29 to 141) infections if air cleaners had not been installed (\supp~\zref{fig:avoided-infections}). Detailed estimations are provided in the \supp~text~\zref{sec:detailed-redcap}.

@@

\begin{figure}[!htpb]
\centering
    \includegraphics{../../results/mol-data/saliva-by-study-condition.pdf}\hspace{.5cm}
    \includegraphics{../../results/env-data/aerosol-number-boxplot.pdf}
    \includegraphics{../../results/epi-data/cases_by_condition.pdf}\hspace{.5cm}
    \includegraphics{../../results/cough-data/coughs-frequency-by-condition.pdf}
    \caption{\textbf{Risk of infection by study condition}. \textbf{(a)}~Number of positive saliva samples. \textbf{(b)}~Daily average aerosol number concentrations as boxplots. \textbf{(c)}~Number of respiratory cases. \textbf{(d)}~Daily average number of detected coughs per minute. ``PP(Yes<No)'' is the posterior probability that the outcome is lower with air cleaners, which is computed based on the posterior samples of the Bayesian models adjusted for observed confounders.}
    \label{fig:infection-risk}
\end{figure}
